The promise of community driven preprints in ecology and evolution

### 2024-04-19 ms/ms.qmd
Spelling error

### *Catious 'open'-mindedness of research findings in preprints*
In additon to speeding up dissemination, preprints can also be a useful way to ensure that research remains open and accessible to the research community because the paper is available online no matter what the open access status of the publication ends up being [@bourne2017ten; @vale2015accelerating]. Using the published articles on *EcoEvoRxiv*, we evaluated the open access status of each paper using....LOSIA?. Most of the published preprints ended up being open access([@fig-pubsummary]A), however, the status of many (i.e., `r sum_is_oa$n[3]` or `r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` or `r sum_is_oa$percent[1]*100`% were not published in open access reserach journals. The level of open access for a paper published in an open access journal also varied widely ([@fig-pubsummary]B).

>>>>

### *Cautious 'open'-mindedness of research findings in preprints*
In additon to speeding up dissemination, preprints can also be a useful way to ensure that research remains open and accessible to the research community because the paper is available online no matter what the open access status of the publication ends up being [@bourne2017ten; @vale2015accelerating]. Using the published articles on *EcoEvoRxiv*, we evaluated the open access status of each paper using....LOSIA?. Most of the published preprints ended up being open access([@fig-pubsummary]A), however, the status of many (i.e., `r sum_is_oa$n[3]` or `r sum_is_oa$percent[3]*100`%) were unknown, and `r sum_is_oa$n[1]` or `r sum_is_oa$percent[1]*100`% were not published in open access reserach journals. The level of open access for a paper published in an open access journal also varied widely ([@fig-pubsummary]B).
